Conjure: Summoning Proxies from Unused Address Space

### 2019-09-26 paper/paper.tex
mask site pass

Any protocol that satisfies these criteria can be used as an effective transport
with \scheme. In this section, we describe various existing protocols (OSSH and obfuscated Obfs4) as well
as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
can be used in \scheme, and evaluate how each meet the necessary requirements.
Table~\ref{tab:applications} compares the application protocols. \scheme uses a modular 
approach to transports because research into proxy detection is ongoing.
Having a variety of supported transports gives clients a quick way to pivot and 
maintain proxy access even when new proxy protocol vulnerabilities are discovered.

@@

Working with currently popular implementations of TLS we overcome the active 
and passive probing challenges by mimicking an existing mask site. To a censor, this site
will be difficult to distinguish from the actual site, making it expensive for
them to block without potentially blocking the real site. TLS connections to the
\scheme station will terminate exactly as connections to the mask site would, with
\scheme acting as a transparent TCP-layer proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-side shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

@@

The \scheme station can determine if the client did this by trial decryption with
the master secret derived from the known seed shared at registration. If it succeeds, the
client has proved knowledge of the seed, and the application can
respond as a proxy. If not, the application simply continues to forward data
between the client and the mask site, in case a clients IP was taken over by
a censor after registration. As the censor does not have knowledge of
the \textbf{seed} used in registration, it cannot coerce the application to
appear as anything besides the mask site.

@@

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a phantom host in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
globally resolves to a single IP address, the censor could also trivially
identify and block the phantom host.

>>>>

Any protocol that satisfies these criteria can be used as an effective transport
with \scheme. In this section, we describe various existing protocols (OSSH and obfs4) as well
as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
can be used in \scheme, and evaluate how each meet the necessary requirements.
Table~\ref{tab:applications} compares the application protocols. \scheme uses a modular 
approach to transports because research into proxy detection is ongoing.
Having a variety of supported transports gives clients a quick way to pivot and 
maintain proxy access even when new proxy protocol vulnerabilities are discovered.

@@

Another option to overcome active and passive probing attacks is to mimic existing TLS sites.
In this application, we simply forward traffic between any connecting clients
and a real TLS site. To a censor, our phantom site
will be difficult to distinguish from the actual ``mask'' site, making it expensive for
them to block without potentially blocking the real site. TLS connections to the
\scheme station will terminate exactly as connections to the mask site would, with
\scheme acting as a transparent TCP-layer proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-side shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

@@

The \scheme station can determine if the client did this by trial decryption with
the master secret derived from the known seed shared at registration. If it succeeds, the
client has proved knowledge of the seed, and the application can
respond as a proxy. If not, the application simply continues to forward data
between the client and the mask site, in case a client's IP was taken over by
a censor after registration. As the censor does not have knowledge of
the \textbf{seed} used in registration, it cannot coerce the application to
appear as anything besides the mask site.

@@

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a phantom host in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a phantom host at an IP address pretends to be a domain that
globally resolves to a single (different) IP address, the censor could also trivially
identify and block the phantom host.
